% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{ZhiYuan Hu}

\basicInfo{
  \email{huzhy5018@gmail.com} \textperiodcentered\ 
  \phone{(+86) 182-218-61528} \textperiodcentered\ 
  \linkedin[Hu Zhiyuan]{https://www.linkedin.com/in/hu-zhiyuan-1ba50798/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Fudan University (FuDan)}, Shanghai, China}{2011.9 -- 2014.7}
\textit{M.S.} in Pure Mathematics(GPA 3.6/4.0) \\
\textit{Main Subjects}: 
Modern Ordinary Differential Equations, Physics and Partial Differential Equations, Aplied Partial Sifferential Wquations, Control Theory Basis
\datedsubsection{\textbf{Lanzhou University(LZU)}, Lanzhou, Ganshu, China}{2007.8 -- 2011.7}
\textit{B.S.} in Pure and Applied Mathematics(GPA 4.01/4.5)\\
\textit{Main Subjects}:
Mathematical Model, Numerical Analysis, Operations Research, Graph Theory, Financial Engineering

\section{\faUsers\ Experience}
\datedsubsection{\textbf{FT Assets Ltd.} Shanghai, China}{2018.01 -- Present}
\role{Data Scientist}{}
Brief introduction:
\begin{itemize}
  \item Constructed, Evaluated and Deploied Credit Default Model; The accuration
	  and KS value of Credit Default Prediction were improved to 80 percent and 45.
  \item Studied, Constructed, Evaluated, Deploied Machine Learning Model of fundmental analysis among Bond, Macro, Commodity, Industry, Stock.   
  \item Designed Web API and Web Online System.
  \item Designed and Constructed Real-Time Stream Processing Module which can Extract, Transform, Load (ETL) Data,  Compute feature and predict for model.	  
\end{itemize}

\datedsubsection{\textbf{Maxent Inc}}{2016.03 -- 2018.01}
\role{Data Scientist}{}
Brief introduction: 
\begin{itemize}
   \item Taked responsible for Anti-Fraud Data Mining project for a state-owned enterprises as Team Leader, which proves if Machine Learning can use for anti-fraud and passed by the client Organization. Main sub-project as follows:
   \begin{itemize}
       \item Clean and Fusion Analysis of Data
       \item Feature Engeering
       \item Graph Mining: Constructed Heterogeneous Network and Homogeneous Network, Applied PageRank algorithm for Homogeneous Network, Constructed One and Two DegreeFeature 
       \item Constructed Score Model(based on Logistic Regression)
   \end{itemize}
   \item Redesigned DFP algorithm for POC(Proof of Concept) which make the accuration achieve 100\%.
   \item Improved Device FingerPrint(DFP) algorithm, Tuned Params for the DFP model, developed algorithm part of DFP model.
   \item Designed anti-charge model for a gaming company which achieved 95\% percent accuration and reduced 5 \% bad debt rate.
   \item Designed ETL(Extract, Transform, Load) System and Visulized data for improving efficency for pre-sales and sales department. 
\end{itemize}

\datedsubsection{\textbf{Ctrip.com}}{2014.10 -- 2016.03}
\role{Data Mining Engneer}{}
Brief introduction:
\begin{itemize}
  \item Analyzed user behavior and differential priced for hotel room.
  \item Analyzed Ctrip brand intrinsic value for pricing strategy of hotel room.
  \item Dynamically adjusted hotel room price according to the relationship betwween saling progress and inventory of hotel room, which increased 8\% revenue per month.
  \item Constructed quantity of hotel room prediction model based on Xgboost and filtered useful factor related to hotel room, which decrease cost hotel room which perchased from hotel owner.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: HQL(Hive SQL)/SQL, Python(Numpy,Scipy,Matplotlib,Seaborn, Pandas), R, Scala/Java, Go, C++/C.
  \item Proficienct in Machine Learning algorithm such as Lasso, LAR, Logistic Regression, Naive Bayes, Decision Treem Random Forest, KNN, SVM, xgboost, Neural Network for Supervised Learning; KMeans, PCA, GMM(Gaussian Mixture Model), HMM(Hidden Markov Model), Descent Clustering for Unsupervised Learning, etc.
  \item Proficient in RDBMS:SQL Server 2008, Mysql, No-sql DataBase: MongoDB, Graph DataBase: Neo4j, Memrory DataBase: Redis.
  \item Mastered in Distributed Computation like Hadoop Eco-system, Spark.
  \item Mastered in Neural Network Computation Platform like tensorflow, Mxnet.	  
  \item Platform: Linux
  \item Development: Spark, Web Service
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1}Prize}, Award on Fudan University Scholarship}{Sep. 2013}
\datedline{\textit{\nth{1} Prize}, Award on National College Students Mathematical Modeling Contest}{Dec. 2010}
\datedline{Other awards, National Inspirational Scholarship}{Sep. 2010}
\datedline{Other awards, Published SCI(Journal of Mathematics and Physics) thesis: Pullback attractors for a nonautonomous nonclassical diffusion equations with time delay}{June. 2011}
\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
 % \item Blog: http://your.blog.me
 % \item GitHub: https://github.com/username
  \item Languages: English - Not Bad, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
